
\section{Introduction}

In \cite{balmer_2019} Balmer constructs a comparison map between the homological spectrum and the Balmer spectrum of a rigidly compactly generated tensor-triangulated category $\C$. After showing this map is always surjective, Balmer displayed his nerves of steel by \emph{not} conjecturing that it is always an isomorphism. Naturally, the community branded this as the ``nerves of steel conjecture''. 

The \emph{homological spectrum}, $\Spch(\Co)$, has points given by the maximal Serre $\otimes$-ideals in the Freyd envelope $\FEo$ of $\C$, while the \emph{Balmer spectrum}, $\Spc(\Co)$, has points given by the prime thick $\otimes$-ideals of $\Co$. The map between them, usually denoted $\phi$, is called the comparison map, and is given by pulling back a homological prime $B\in \Spch(\Co)$ along the restricted Yoneda embedding 
\begin{align*}
    y\: \C &\to \FE \\
    C &\longmapsto \Hom_\C(-,C)_{\mid \Co}
\end{align*}
The surjectivity of $\phi$, as proven by Balmer in \cite[3.9]{balmer_2019} is somewhat surprising, as one is used to there being more primes than the maximal ones. The \emph{nerves of steel conjecture} states that $\phi$ is also injective. 

\begin{conjecture}[{\cite[5.15]{balmer_2019}}]
    \label{conj:nerves-of-steel}
    The map $\phi\: \Spch(\Co)\to \Spc(\Co)$ is an isomorphism. 
\end{conjecture}

The singular goal of this paper is to prove this conjecture in the affirmative. Our approach combines the results from \cref{ch:4} with the work of Patchkoria--Pstr\a{}gowski in \cite{patchkoria-pstragowski_2021}. In the former we proved a classification result for localizing subcategories along a $t$-structure. In the latter the authors study a prestable enhancement of the Freyd envelope by using sheaves of spaces rather than sheaves of abelian groups. As $tt$-geometry happens in the stable world, and we want access to $t$-structures, we have to enlarge the category even further, by using sheaves of spectra. 

The category of \emph{spherical presheaves} on $\C$, denoted $\sFE$, has a naturally occuring $t$-structure, where the connected component $\sFE\geqz$ is a prestable enhancement, and the heart is the category of modules over $\Co$, i.e., $\FE$. The compact objects in the heart is precicely the classical Freyd envelope of $\C$, the compact objects in $\sFE\geqz$ recovers the \emph{prestable Freyd envelope} of \cite{patchkoria-pstragowski_2021}, and we define the \emph{stable Freyd envelope} of $\C$ to be the compact objects in $\sFE$. 

As the full category of spherical presheaves is a rigidly compactly generated presentably symmetric monoidal stable $\infty$-category, it has a well behaved Balmer spectrum, which we call the \emph{homological Balmer spectrum} of $\C$: 
\[\SpcH(\Co) := \Spc(\sFEo).\]

This setup gives us access to both the classification results of \cref{ch:4} and some structural results about enhanced Freyd envelopes from \cite{patchkoria-pstragowski_2021}. We use these ideas to prove that there exists a set-theoretical map from the homological spectrum to the homological Balmer spectrum. 

\begin{introthm}[{\ref{thm:existence-of-Phi}}]
    \label{introthm:A}
    There is a map of sets $\Phi\: \Spch(\Co)\to \SpcH(\Co)$.
\end{introthm}

We call this map the \emph{stable comparison map}, and its existence relies on a monoidal version of our main result from \cite{aambo_2024_localizing}, which we cover in \cref{app:A}, together with a more detailed analysis of the compact objects at the stable, prestable and abelian levels. 

Our main result, from which \cref{conj:nerves-of-steel} will be a corollary, is that $\Phi$ is a very nice map indeed. 

\begin{introthm}[{\ref{lm:Phi-is-injective}, \ref{lm:Phi-is-continuous-and-closed}, \ref{prop:Phi-factors-phi}}]
    \label{introthm:B}
    The stable comparison map $\Phi$ is a topological embedding, which factors the comparison map $\phi$ via a surjective map $f$. 
\end{introthm}

Barthel, Heard and Sanders prove in \cite[4.5]{barthel_heard_sanders_2022} that $\phi$ is a bijection if and only if $\Spch(\Co)$ is a $T_0$ space. By \cref{introthm:B} the homological spectrum $\Spch(\Co)$ is a subspace of $\SpcH(\Co)$, which \emph{is} $T_0$. Hence, as any subspace of a $T_0$ space is itself $T_0$, the nerves of steel conjecture follows immediately. 

\begin{introthm}[{\ref{thm:nerves-of-steel}}]
    \label{introthm:C}
    The comparison map $\phi\: \Spch(\Co)\to \Spc(\Co)$ is a bijection. 
\end{introthm}

The map $f\: \SpcH(\Co)\to \Spc(\Co)$ is surjective, but unlike $\phi$ it is not an isomorphism. Hence, there are no need for any ``spectral nerves of steel'' to not conjecture that it is. This means that $\SpcH(\Co)$ has access to more refined information about $\C$ compared to its Balmer spectrum $\Spc(\Co)$, and thus serves as a reasonable object of future study. 

\textbf{Acknowledgements:} I want to thank my supervisor Drew Heard for making me aware of this conjecture, and for encouragement along the way. I also want to thank my academic brother Marius Nielsen for always answering my questions and helping me, and the rest of the PhD-students in the topology group at NTNU for fun and interesting discussions. I also want to thank Nikoline Hassing for her continued enthusiastic moral support, and to thank Fernando Abellan for hallway shenanigans and help with some of the category theory. Finally I want to thank the beautiful awe-inspiring mountains in Storlidalen, as featured on the front page. The picture is taken roughly 20 meters before the proof-strategy for this paper hit me while skiing alone right before christmas last year. This work is part of my thesis, partially supported by grant number TMS2020TMT02 from the Trond Mohn Foundation. 

\textbf{Conventions:} It is perhaps more standard to use tensor-triangulated categories in the $tt$-geometry literature, but, as we will see throughout the paper, it makes no difference to the story. As the author is more familiar with the $\infty$-categorical context, we have decided to that framework. Hence, we will freely use the language of $\infty$-categories, as developed in \cite{lurie_09} and \cite{Lurie_HA}. Throughout this paper, $\C$ will denote a rigidly compactly generated symmetric monoidal stable $\infty$-category, also called a big $tt$-category. The full subcategory of compact objects, which as $\C$ is rigidly generated coincides with the dualizable objects, will be denoted $\C^\omega$. We will try to consistently denote general objects by upper-case letters, $C\in \C$, and compact objects by lower-case letters, $c\in \C$. 

