

\section{Classification of localizing ideals along t-structures}
\label{app:A}

The goal of this appendix is to make an extension of our main result from \cref{ch:4} to the monoidal setting. 

We fix a presentably symmetric monoidal stable $\infty$-category $\D$, equipped with a $t$-structure $(\D\geqz, \D\leqz)$ compatible with the monoidal structure and filtered colomits. Such a $t$-structure on $\D$ induces by definition a symmetric monoidal structure on $\D\geqz$, such that $\Sigma^\infty\: \D\geqz\to \D$ is symmetric monoidal. Hence, $\D\geqz$ is a symmetric monoidal Grothendieck prestable $\infty$-category. 

Our goal is to prove that there are one-to-one correspondences
\[\piexactideals \simeq \separatingideals \simeq \heartideals\]
In \cref{ch:4} we prove this without the existence of a monoidal structure, working with localizing subcategories instead. We will prove this monoidal version in several steps, starting with the right-side correspondence between ideals in the prestable world and ideals in the abelian world. 

\begin{lemma}
    \label{lm:monoidal-correspondence-prestable-abelian}
    The heart construction $\L\geqz \mapsto \L^\heart$ gives a one-to-one correspondence 
    \[\separatingideals \simeq \heartideals\]
\end{lemma}
\begin{proof}
    Note first, that without the $\otimes$-ideal assumption, this is a result due to Lurie --- see \cite[C.5.2.7]{lurie_SAG}. So it remains only to show that a separating localizing subcategory $\L\geqz$ is an $\otimes$-ideal if and only if $\L^\heart$ is a localizing $\otimes$-ideal. 

    Let $\L^\heart$ be a localizing $\otimes$-ideal of $\D^\heart$. The associated separating localizing subcategory $\L\geqz$ is the full subcategory of $\D\geqz$ consisting of the objects $X\in \D\geqz$ such that $\pi_k X\in \L^\heart$ for all $k$. As $\pi_k X \simeq \pi_0\Sigma^{-k}$, and $\L^\heart$ is closed under shift and $\L$ is closed under desuspension, the category $\L\geqz$ coincides with the inverse image of $\L^\heart$ under the functor $\pi_0 \: \D\geqz\to \D$. 
    
    By \cite[A.12]{antieau_nikolaus_2020} this functor $\pi_0$ is symmetric monoidal, hence the preimage of an $\otimes$-ideal is an $\otimes$-ideal. To be precise: for $L\in \L\geqz$ and $D\in \D\geqz$ we have, as $\L\geqz$ is separating, $L\otimes D \in \L\geqz$ if and only if 
    \[\pi_0(L\otimes D) \simeq \pi_0 L \otimes \pi_0 D \in \L^\heart,\]
    which then holds as $\L^\heart$ is an ideal and $\pi_0 L\in \L^\heart$. 

    Now, assume that $\L\geqz$ is a separating localizing ideal of $\D\geqz$. By Lurie's correspondence we know that $\L^\heart$ is a localizing subcategory of $\D^\heart$. Any object in the heart $\L^\heart$ is by definition of the form $\pi_0 L$ for some $L\in \L\geqz$, similarily for any object in $\D\geqz$. Hence, we can let $\pi_0 L \in \L^\heart$ and $\pi_0 D\in \D^\heart$. As $\L\geqz$ is separating we have 
    \[\pi_0 D \otimes \pi_0 L \simeq \pi_0(D \otimes L) \in \L^\heart\] 
    if and only if $D\otimes L$ is in $\L^\heart$. As $\pi_0 L \in \L^\heart$, we know, again by the fact that $\L\geqz$ is separating, that $L\in \L\geqz$. Hence, as $\L\geqz$ was assumed to be an $\otimes$-ideal we get $D\otimes L \in \L\geqz$, which proves that also $\L^\heart$ is an ideal. 
\end{proof}

It remains to prove that the correspondence 
\[\piexactD \simeq \separatingD\]
established in \cref{ch4:thm:main} also restricts to $\otimes$-ideals. The corrspondence is given by the mutually inverse pair of maps $(-)\geqz$ and $\Sp(-)$. Hence, if we show that both of these preserve being an ideal we will get our result. 

\begin{lemma}
    \label{lm:connected-part-of-ideal-is-ideal}
    If $\L\subseteq \D$ is a $t$-exact localizing ideal, then the connected part $\L\geqz$ is a localizing ideal in $\D\geqz$.  
\end{lemma}
\begin{proof}
We know that $\L\geqz$ is a localizing subcategory of $\D\geqz$ by \cref{ch4:cor:t-exact-corresponds-to-prestable-localizing}, and that $\D\geqz$ inherits a symmetric monoidal structure from $\D$ by definition. Given a generic object $\tau\geqz L \in \L\geqz$ and a generic object $\tau\geqz D\in \D\geqz$ we have $\tau\geqz L \otimes \tau\geqz D \in \D\geqz$. As $\L$ was assumed to be $t$-exact, it is in particular $t$-stable, meaning that $\tau\geqz L \in \L$ for any $L\in \L$ --- see \cref{ch4:def:t-stable-localizing-subcategory} and \cref{ch4:lm:t-exact-then-t-stable-kernel} for details. Since $\L$ is an ideal, this means that $\tau\geqz L \otimes \tau\geqz D \in \L$, as it is closed under tensoring with objects in $\D$. Hence, we have 
\[\tau\geqz L \otimes \tau\geqz D \in \L \cap \D\geqz = \L\geqz\]
by \cite[1.3.19 ]{beilinson-bernstein-deligne_1983} --- see also \cref{ch4:rm:t-stable-truncation-homotopy-the-same-functors}
\end{proof}

To show that the inverse map $\Sp(-)$ also preserves ideals we first make a convenient rephrasing of the ideal property for any presentably symmetric monoidal $\infty$-category, not neccessarily prestable or stable. By $\otimes$-ideal we here mean that $L\in \L$ implies $L\otimes C \in \L$ for all $\C\in \C$. Below, $\otimes^L$ denotes the Lurie tensor product in $\PrL$. 

\begin{lemma}
    \label{lm:categorical-ideal-property}
    Let $\E$ be a presentably symmetric monoidal $\infty$-category, and $\L\subseteq \E$ a presentable full subcategory. Precomposing with the inclusion we get a functor 
    \[\mu\: \L\otimes^L \E \to \E\otimes^L\E \to \E.\]
    The subcategory $\L$ is an $\otimes$-ideal if and only if $\mu$ factors through the inclusion $\L\hookrightarrow \E$. 
\end{lemma}
\begin{proof}
    Note that, if we replace the Lurie tensor product $\otimes^L$ with the cartesian one, $\times$, then this it literally just the definition of an ideal, as the functor $\mu_\times\: \L\times \E \to \E$ sends $(L,E) \mapsto L\otimes E$. By assumption the symmetric monoidal structure on $\E$ preserves colimits separately in each variable, meaning that $\mu_\times$ factors uniquely through $\mu$. Hence, as $\L\hookrightarrow \E$ is preserves colimits, $\mu$ factors through $\L$ if and only if $\mu_\times$ does, finishing the proof. 
\end{proof}

We can now prove the final part of our wanted correspondence. 

\begin{lemma}
    \label{lm:stabilizing-ideal-gives-ideal}
    If $\L\geqz$ is a localizing $\otimes$-ideal in $\D\geqz$, then its stabilization $\L$ is a $t$-exact localizing ideal of $\D$. 
\end{lemma}
\begin{proof}
    First, note that $\L = \Sp(\L\geqz)$ is a $t$-exact localizing subcategory by \cref{ch4:cor:t-exact-corresponds-to-prestable-localizing}, hence it remains only to show that it is an ideal. The stabilization functor $\Sp(-)\: \mathrm{Groth}\to \PrLs$ is symmetric monoidal with respect to the Lurie tensor product, hence it sends the composite 
    \[\L\geqz\otimes \D\geqz \to \D\geqz\otimes \D\geqz \to \D\geqz\]
    to 
    \[\L\otimes \D \to \D\otimes \D \to \D.\]
    As the symmetric monoidal structures on $\D\geqz$ and $\L\geqz$ was induced from $\D$, we do recover the original symmetric monoidal structure in this process. The former functor factors through $\L\geqz$ by \cref{lm:categorical-ideal-property}, hence the latter factors through $\L$. This means that it is an ideal, again by \cref{lm:categorical-ideal-property}. 
\end{proof}

We can then conclude with our wanted classification. 

\begin{theorem}
    \label{thm:classification-ideals-t-structure}
    There are one-to-one correspondences
    \begin{center}
        \begin{tikzcd}
            \piexactideals \arrow[r, yshift=2, "(-)\geqz"] & \separatingideals \arrow[r, "(-)\leqz"] \arrow[l, yshift=-2, "\Sp(-)"] & \heartideals
        \end{tikzcd}
    \end{center}
\end{theorem}
\begin{proof}
    The right hand map is a one-to-one correspondence by \cref{lm:monoidal-correspondence-prestable-abelian}. The two maps on the left are mutually inverse equivalences due to \cref{ch4:lm:pi-exact-then-separating} and \cref{ch4:lm:separating-then-pi-exact}, together with \cref{lm:connected-part-of-ideal-is-ideal} and \cref{lm:stabilizing-ideal-gives-ideal}.
\end{proof}