

\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

Chromatic homotopy theory aims to study the category of spectra, $\Sp$, by splitting it into an infinite family of colors---like shining white light through a prism. Each individual color is specified by a wavelength, or periodicity, given by $2p^n-2$, where $p$ is a prime number and $n$ a non-negative integer called the chromatic height. The corresponding piece of $\Sp$ is the category of $\Kpn$-local spectra, $\Sp_\Kpn$, where $\Kpn$ is a $2p^n-2$-periodic spectrum called height $n$ Morava $K$-theory. 

The overarching goal of this thesis is to broaden our understanding of the category $\Sp_\Kpn$, which we do by studying its relationship to three different algebraic structures. These three connections are constructed in their own research paper, which constitutes the lion's share of the content of the thesis. Let us describe our main findings:

At chromatic height $0$ we have $K_p(0) = H\Q$, giving us rational stable homotopy theory---a completely algebraic theory. It is known that the analogous statement fails at positive chromatic heights: $\Sp_\Kpn$ is not algebraic. However, our first paper uses Patchkoria--Pstr\a{}gowski's version of Franke's algebraicity theorem to prove that $\Sp_\Kpn$ is \emph{exotically} algebraic when $p$ is much larger than $n$. More precisely we prove that $\Sp_\Kpn$ is exotically equivalent to $\Fr\np\Inc$---the Franke category of derived $I_n$-complete comodules over $E_*E$. 

In the second paper we prove a version of Positselski's comodule-contramodule correspondence for coidempotent cocommutative coalgebras in a presentable $\infty$-category $\C$. When $\C$ is stable, we show that this recovers local duality in the sense of Hovey--Palmieri--Strickland, allowing us to describe the category of $\Kpn$-local spectra as contramodules over the monochromatization of the sphere spectrum. We also define an $\infty$-categorical analog of Positselski's contramodules over topological rings, and prove that $\Sp_\Kpn$ is equivalent to the category of contramodules over $L_\Kpn \S$. 

Let $\C$ be a stable $\infty$-category with a $t$-structure $(\C\geqz, \C\leqz)$. In the third paper we classify which localizing subcategories of $\C$ that are completely determined by the Grothendieck abelian heart $\C\geqz \cap \C\leqz = \C^\heart$. This generalizes previous work by Takahashi, and extends a similar classification due to Lurie. It also allows us to construct a deformation between $\Sp_\Kpn$ and $\Fr\np\Inc$, which we use to prove a symmetric monoidal version of the exotic equivalence from the first paper. 




% This thesis consists of three papers---all focused on understanding certain features of localizing subcategories; all motivated by understanding features of chromatic homotopy theory. 

% Our first paper uses Patchkoria--Pstr\a{}gowski's version of Franke's algebraicity theorem to prove that monochromatic homotopy theory is completely algebraic when the prime $p$ is large compared to the chromatic height $n$. In particular, we prove that the category of spectra, localized the Morava $K$-theory spectrum $K_p(n)$, is equivalent to the derived $I_n$-complete objects in Franke's category of periodic comodules over $E_*E$---the Hopf algebroid associated to height $n$ Morava $E$-theory. 

% In the second paper we introduce contramodules over a cocommutative coalgebra in a presentably symmetric monoidal $\infty$-category. When the coalgebra $C$ is coidempotent, we prove that there is a symmetric monoidal duality between comodules and contramodules over $C$, which we call Positselski duality. Furthermore, when the ambient category is stable and compactly generated by dualizable objects, this duality recovers local duality in the sense of Hovey--Palmieri--Strickland, allowing us to describe the category of $K_p(n)$-local spectra as contramodules over the monochromatization of the sphere spectrum. 

% The third paper studies how certain localizing subcategories compatible with a given $t$-structure on a stable $\infty$-category $\C$, can be classified by using the associated Grothendieck prestable $\infty$-category $\C\geqz$ and the associated Grothendieck abelian heart $\C^\heart$. In particular, we prove that there is a one-to-one correspondence between $t$-structure compatible localizing subcategories in $\C$, and prestable localizing subcategories of $\C\geqz$. This allows us to extend a result of Lurie to the stable setting, and prove a classification result for these localizing subcategories. 


\newpage 
\section*{Sammendrag}
\addcontentsline{toc}{section}{Sammendrag}

Kromatisk homotopiteori forsøker å studere kategorien av spektra, $\Sp$, ved å dele den opp i et uendelig antall farger---som å skinne hvitt lys gjennom et prisme. Hver individuelle farge har en bølgelengde, eller periodisitet, gitt som $2p^n-2$, der $p$ er et primtall og $n$ er et ikke-negativt heltall kalt den kromatiske høyden. Den korresponderende delen av $\Sp$ er kategorien av $\Kpn$-lokale spektra, $\Sp_\Kpn$, der $\Kpn$ er et $2p^n-2$-periodisk spektrum kalt Morava $K$-teori av høyde $n$. 

Det overordnede målet med denne avhandlingen er å utvide vår forståelse av kategorien $\Sp_\Kpn$, noe vi gjør ved å studere dens forhold til tre ulike algebraiske strukturer. Disse tre koblingene konstrueres i hver sin forskningsartikkel, som utgjør brorparten av innholdet i avhandlingen. La oss beskrive hovedfunnene: 

Når den kromatiske høyden er $0$ har vi $K_p(0) = H\Q$, som gir oss rasjonal stabil homotopiteori---en fullstendig algebraisk teori. Det er kjent at den tilsvarende påstanden ikke er sann ved positive kromatiske høyder: $\Sp_\Kpn$ er ikke algebraisk. I avhandlingens første artikkel viser vi likevel at $\Sp_\Kpn$ er \emph{eksotisk} algebraisk når $p$ er mye større enn $n$, ved å anvende Patchkoria--Pstr\a{}gowskis versjon av Frankes algebraisitetsteorem. Mer presist viser vi at $\Sp_\Kpn$ er eksotisk ekvivalent til $\Fr\np\Inc$---Frankes kategori av derivert $I_n$-komplette komoduler over $E_*E$. 

I den andre artikkelen beviser vi en versjon av Positselskis komodul-kontramodul-korrespondanse for koidempotente kokommutative koalgebraer i en presenterbar $\infty$-kategori $\C$. Når $\C$ er stabil viser vi at dette gjenskaper Hovey--Palmieri--Stricklands lokal dualitet, som lar oss beskrive kategorien av $\Kpn$-lokale spektra som kontramoduler over monokromatiseringen av sfærespektumet. Vi definerer også en $\infty$-kategorisk versjon av Positselskis kontramoduler over en topologisk ring, og viser at $\Sp_\Kpn$ er ekvivalent til kategorien av kontramoduler over $L_\Kpn \S$. 

La $\C$ være en stabil $\infty$-kategori med en $t$-struktur $(\C\geqz, \C\leqz)$. I den tredje artikkelen klassifiserer vi hvilke lokaliserende underkategorier av $\C$ som er fullstendig bestemt av det Grothendieck-abelske hjertet $\C\geqz \cap \C\leqz = \C^\heart$. Dette generaliserer tidligere resultater av Takahashi, og utvider en lignende klassifisering av Lurie. Det lar oss også konstruere en deformasjon mellom $\Sp_\Kpn$ og $\Fr\np\Inc$, som vi bruker til å vise en symmetrisk monoidal versjon av den eksotiske eksivalensen fra den første artikkelen. 

% Denne avhandlingen består av tre artikler---alle fokusert på å forstå visse egenskaper av lokaliserende underkategorier; alle motivert av å forstå egenskaper iboende kromatisk homotopiteori. 

% Vår første artikkel bruker Patchkoria--Pstr\a{}gowskis versjon av Frankes algebraisitetsteorem til å bevise at monokromatisk homotopiteori er fullstendig algebraisk når primtallet $p$ er mye større enn den kromatiske høyden $n$. Mer presist viser vi at kategorien av spectra lokalisert ved Morava $K$-teorispektrumet $K_p(n)$, er ekvivalent til $I_n$-komplette objekter i Frankes kategori av periodiske komodules over $E_*E$---Hopf algebroiden assosiert til Morava $E$-teori med høyde $n$. 

% I den andre artikkelen introduserer vi kontramoduler over en kokommutativ koalgebra i en presenterbar symmetrisk monoidal $\infty$-kategori. Når koalgebraen $C$ er koidempotent viser vi at det er en symmetrisk monoidal dualitet mellom komoduler og kontramoduler over $C$, som vi kaller Positselski-dualitet. Videre viser vi at dersom bakgrunnskategorien er stabil og kompakt-generert av dualiserbare objekter, så gjennskaper dette Hovey--Palmieri--Stricklands teori om lokal dualitet, som lar oss beskrive kategorien av $K_p(n)$-lokale spektra som kontramoduler over monokromatiseringen av sfærespektumet. 

% Den tredje artikkelen studerer hvordan lokaliserende underkategorier som er kompatible med en gitt $t$-struktur på en stabil $\infty$-kategori $\C$, kan klassifiseres via den tilhørende Grothendieck-prestabile $\infty$-kategorien $\C\geqz$ og det Grothendieck-abelske hjertet $\C^\heart$. Vi viser at det er en en-til-en korrespondanse mellom disse $t$-struktur-kompatible lokaliserende underkategoriene av $\C$, og prestabile lokaliserende underkategorier av $\C\geqz$. Dette lar oss utvide et resultat av Lurie til den stabile settingen, og bevise et klassifiserings resultat for disse lokaliserende underkategoriene. 


