
\section*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

During the last four years I have had the pleasure of working with, and getting help from, a large number of very lovely people; without their support, guidance, expertise and drive, this thesis would never have been made. 

\subsection*{Mathematics}

First off, I want to thank my supervisor Drew Heard. He has been completely invaluable in both mathematical and personal support, and have fundamentally taught me how to be a mathematician. Already after our third meeting I wrote in my diary ``I think I have struck supervisor gold''. He has always supported me in following my mathematical interests, and has always been willing to discuss and entertain my ideas and questions. It has also been nice to have someone to talk to about skiing, job-applications, traveling, conferences, and a whole lot of other relevant and irrelevant topics. 

Next I want to thank Marius Nielsen. I think it is safe to say that my research projects would have taken much longer to finish had it not been for Marius answering all of my many questions, helping with proof-reading, sharing ideas, and being generally very supportive---I could not have asked for a better office-mate! The rest of the people in the topology group also deserve their credits. I want to thank Fernando Abellán for continuous hallway shenanigans; Tallak Manum for always ranting about everything; Abigail Linton for countless interesting discussions on the Norwegian language; Clover May for discussions about equivariance, computations and moral support in the hunt for jobs. A huge thanks also to 
Fredrik Bakke, 
Erlend Bergtun, 
Sigurd Gaukstad, 
Rune Haugseng,
Knut Bjarte Haus, 
Alice Hedenlund, 
William Hornslien, 
Eiolf Kaspersen, 
Sebastian Martensen, 
Louis Martini,
Trygve Poppe Oldervoll, 
Therese Strand, 
Marius Thaule and 
Gereon Quick, 
for helpful conversations, fun lunch breaks and evenings of beer-drinking.

Outside the topology group at NTNU I have benefitted a lot from both conversations and other activities with a lot of different people. I want to thank 
Elias Klakken Angelsen, 
Tobias Barthel, 
Shay Ben-Moshe, 
Thomas Blom, 
Guy Boyde,
Erlend Due Børve, 
Sebastian Chenery, 
Julius Frank, 
Itamar Mor, 
Sven van Nigtevecht, 
Lucas Piessevaux, 
Luca Pol, 
Julie Rasmusen and 
Dominik Trnka, 
and sincerely apologize to the long list of people I have not mentioned, but who have still contributed to the amazing time I have had the last four years. 

I have also been privileged enough to be able to visit other universities to learn and discuss mathematics. A warm thanks goes out to the entire GeoTop center at Copenhagen University, where I stayed for almost five months. A special thanks to Florian Riedel for interesting discussions about math, fun conversations about hiking and nature, as well as bouldering sessions. A warm thanks also goes out to Greg Stevenson at Aarhus University, who invited me to spend a couple weeks there. My stay in Aarhus grew into the second paper of this thesis, and gave me lots of interesting mathematics to think about. Lastly I want to thank Irakli Patchkoria for inviting me to the University of Aberdeen to discuss parts of his works on algebraicity. He has also been very supportive and interested in my projects, and have always made sure to discuss them whenever we have met at conferences, or randomly at the airport in Amsterdam. 

Finally, this thesis itself has had considerable help in its production---The individual papers before originally being made public, and the rest of the material in the final stages of production. Even though the individual papers thank the people involved, I repeat the list here. The first paper benefitted a lot from conversations with Marius Nielsen and Irakli Patchkoria. They, as well as Drew Heard, also helped proof-read the paper, for which I thank them deeply. I also want to thank Piotr Pstr\a{}gowski for finding a mistake in the original version of the first paper, and the anonymous referee for very thorough and helpful feedback which greatly elevated the presentation of the material. The second paper would not exist were it not for Greg Stevenson and Sergey Arkhipov, who introduced me to the notion of a contramodule. In proof-reading both the second and third paper, I again had great help from Drew Heard and Marius Nielsen. The addendum to the second paper is indebted to Florian Riedel, who taught me a lot about the interactions between coalgebras, duality and costabilization. The addendum to the third paper has benefitted a lot from conversations with Marius Nielsen, Sven van Nigtevecht, Paul VanKoughnett and Robert Burklund. The presentation of the material in the introduction was greatly helped by the watchful eyes of Karl Kristian Ladegård Lockert. 


\subsection*{Organization, outreach and teaching}

Even though this thesis only focuses on the mathematics and research I have done, I feel like this is a good opportunity to thank all of the other people who I have worked with, and who has helped me in non-mathematical endeavors. 

First off I want to thank my Young Homotopy-theorist Online Meeting co-organizer: Julie Rasmusen. She has been a pleasure to work with, and we always have fun when we meet. I also want to thank Endre Rundsveen for co-organizing the PITA seminar, and Sarah Petersen for letting me assist in the eCHT Hopf ring seminar. I also want to thank all of the speakers at the seminars, for using your valuable time to present your research, and to all of the people attending. 

I also want to thank the unofficial outreach committee at the Department of Mathematical Sciences---in particular Hans Heum, Karl-Mikael Perfekt, Emma Sofie Skarstein and Laertis Vaso---who have dedicated their time and resources into creating great outreach activities at several events. I am particularly proud of our effort when organizing \emph{The Art of Mathematics} at the HYFER festival, and have learnt a lot by working with every one of you. It should also be mentioned that we could not have done all our work without the direct support from our department head, Einar Rønquist. He has alway been very supportive of my and our outreach activities, and has given us funding and resources for several projects. I have also had a great deal of help from different communications experts. In particular I want to thank Margrethe Meyer Bratt, for pushing me to do more events, always having my back and spotting new opportunities, as well as Ragnhild Angell Gimse Storrø and Thea Rustad for several collaborations. 

Over the years I have benefitted a lot from conversations with Marius Thaule, who has helped me navigate the world of teaching, managing students and good practices for making exams. 

Finally I want to give my deepest thanks to Mette Langaas. Mette was the one who pushed me into several teaching opportunities that are usually not available for PhD students. I was given the opportunity to teach large courses, and was given a lot of freedom and responsibility in course development. Her confidence in my abilities, and general enthusiasm has made me grow a lot as a person and as an educator. I will for ever be grateful for all that Mette has done for me, and for our many discussions about teaching philosophy, teaching in general, and all steps of the Norwegian mathematics-education system.  

\subsection*{Family and friends}

Without the endless support from family and friends this thesis, and the individual papers, would never have existed. I am extremely lucky to have a family that always supports what I do, and encourages me to follow my interests and what brings me joy. I want thank my dad, Kåre Aambø, for always being there for me; for always inviting me to cabin trips; for inviting me to lunches and dinners in stressful work periods; for joining me on back-country and cross-country skiing trips; for supportive conversations and helping me through tough times. I want to thank my mom, Trine Knutsen for countless discussions about university politics and the state of Norwegian academia, but most of all for her endless support in all that I do. I also want to thank my sister Sigrid Aambø and her fiancé Kris Mato, for fun times at the cabin, and for many incredible dinners over the last years. Lastly, I want to thank my grandparents Kari Vik Knutsen and Knut Knutsen, for always having a place for me to stay, and the rest of my broader family for their continued interest and support. 

I also have a lot of friends and band-mates that deserve to be thanked: 
Sondre Bolland, 
Espen Oseid Danielsen, 
Håkon Grønning, 
Yngve Lyngstad Hovind, 
Simen Håpnes, 
Kasper Kvam, 
Roar Nubdal, 
Halvor Nygård, 
Sander Selsbak, 
Haakon Skogstad, 
Tobias Barstad Sæterås, 
and the boys from Aphzelia, Hypermass, Stray, Kulde, Axe Toss and HYNU, as well as all of the amazing people I have had the pleasure to befriend through Delta. They have helped me stay sane, pulled me out of my head, let me sleep on their couches, organized cabin trips, let me explore music and creativity and play live-shows, and lots lots more. A special thanks goes to Karl Kristian Ladegård Lockert, who has been a constant sparring partner for ideas and learning new things, and has kept me active by introducing me to bouldering, and bouldered with me routinely ever since. 

Lastly, and perhaps most importantly, my partner Nikoline Hassing. I cannot begin to describe how her relentless support and help have benefitted me these last years. Having someone so safe, supporting and confident in my abilities has been incredibly important for me. Her family also deserves a shout-out, for always taking good care of us, and helping us with anything we need. I will be forever indebted to Nikoline for all that she has done for me. 


